Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-21 R0V0.tex
Changes on the notation of the metric and the derivative of the geodesic

Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $\gamma:[0,1]\to\mathbb{R}^n$ connecting $x_0=\gamma(0)$ to $x_1=\gamma(1)$. The \emph{length} and \emph{energy} of $\gamma$ are, respectively, defined by the values
\begin{equation*}
	\ell(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}\,ds\ \text{and}\ e(\gamma)=\int_0^1|\gamma'(s)|_{\gamma(s)}^2\,ds\;.
\end{equation*}
The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them. This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem
\begin{equation}\label{eq:geodesic formulation}
	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma)\;.
\end{equation}

@@

Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every $x_0$ and $x_1\in\mathbb{R}^n$, there exist a smooth geodesic curve $\gamma:[0,1]\to\mathbb{R}^n$ connecting them. This implies that the solution $k^\ast$ to the integral equation
\begin{equation}\label{eq:contracting feedback law}
	k^\ast(t,s)=u^\ast(t)+\int_0^s K(\gamma(\sigma),k^\ast(t,\sigma))\gamma'(\sigma)\,d\sigma\;,
\end{equation}
where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.

@@

\begin{theorem}\label{thm:main result}
	If there exist smooth functions $W:\mathbb{R}^n\to\mathbb{R}^{n\times n}$ and $Y:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{m\times n}$ such that $W=W^\top\succ0$, $W$ is block-diagonal, $Y\in\Xi$ and the pair $(W,Y)$ is a solution to the MI \eqref{eq:MI formulation}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N \varphi_i'(s_i)^\top M_i(\varphi_i(s_i))\varphi_i'(s_i)}\,ds\;.
	\end{equation}

@@

	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
	\begin{equation}\label{eq:K ODE}
		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma'(s)=:\overline{K}(t,s,k^\ast)\;.
	\end{equation}
	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$. It remains to show that this interval of existence can be extended on $[0,1]$. In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.

>>>>

Let $\Gamma(x_0,x_1)$ be the set of piecewise-smooth curves $\gamma:[0,1]\to\mathbb{R}^n$ connecting $x_0=\gamma(0)$ to $x_1=\gamma(1)$. The \emph{length} and \emph{energy} of $\gamma$ are, respectively, defined by the values
\begin{align*}
	\ell(\gamma)=&\ \int_0^1\left|\gamma_s(s)\right|_{\gamma(s)}\,ds\\
	e(\gamma)=&\ \int_0^1V\left(\gamma(s),\gamma_s(s)\right)\,ds\;.
\end{align*}
The Riemannian distance between $x_0$ and $x_1$, denoted as $\mathbin{\mathtt{dist}}(x_0,x_1)$, is defined as the curve with the smallest length connecting them. This curve is said to be a \emph{geodesic} and it is the solution to the optimization problem
\begin{equation}\label{eq:geodesic formulation}
	\mathbin{\mathtt{dist}}(x_0,x_1)=\inf_{\gamma\in\Gamma(x_0,x_1)}\ell(\gamma)\;.
\end{equation}

@@

Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every $x_0$ and $x_1\in\mathbb{R}^n$, there exist a smooth geodesic curve $\gamma:[0,1]\to\mathbb{R}^n$ connecting them. This implies that the solution $k^\ast$ to the integral equation
\begin{equation}\label{eq:contracting feedback law}
	k^\ast(t,\sigma)=u^\ast(t)+\int_0^\sigma K(\gamma(s),k^\ast(t,s))\gamma_s(s)\,ds\;,
\end{equation}
where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.

@@

\begin{theorem}\label{thm:main result}
	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system:differential}, then there exists a solution to Problem~\ref{problem formulation}.
\end{theorem}

@@

	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N V_i\left(\varphi_i(s_i),\tfrac{\partial \varphi_i}{\partial s_i}(s_i)\right)}\,ds\;.
	\end{equation}

@@

	From the fundamental theorem of calculus, Equation \eqref{eq:contracting feedback law} is equivalent to the differential equation
	\begin{equation}\label{eq:K ODE}
		\frac{dk^\ast}{ds}(t,s)=K(\gamma(s),k^\ast(t,s))\gamma_s(s)=:\overline{K}(t,s,k^\ast)\;.
	\end{equation}
	which has a unique solution defined of a maximal interval of existence, for every initial condition, due to the regularity of the functions $K$ and $\gamma$. It remains to show that this interval of existence can be extended on $[0,1]$. In other words, show that there exist no $\bar{s}\in[0,1]$ such that $k^\ast(t,s)$ tends to infinity, as $s$ tends to $\bar{s}$.
